### 2018-06-26 Thesis/Parts/Future_work/Future_work.tex
Future work addition

\subheader{TF-IDFs performance point}
In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts. This leads to the question, how do unique token count, token count and vocabulary size relate for TF-IDF? Is there a point in at which we can expect that TF-IDF will be able to rank items in the top-10? If this is the case, we can skip the TF-IDF calculations in certain situations, saving time and costs.

@@

\subheader{TF-IDF top-cutoff}
In our research we used a dataset from which we removed the top 1k words, together with everything beyond 6k. This dataset did not perform well in our research, future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance. Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.
\end{document}

>>>>

\subheader{TF-IDFs performance point}
In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts. This leads to the question, how do token count and unique token count relate for TF-IDF? Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform? If this relation is found,  we could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, saving time and costs.

@@

\subheader{TF-IDF top-cutoff}
In our research we used a dataset from which we removed the top 1k words, together with everything beyond 6k. This dataset did not perform well in our research, future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance. Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search term itself will contain a small amount of tokens, as our research showed, embeddings perform better in this situation. Future work could try to combine these findings, by collecting a large amount of words, resembling the meaning (captured by the embeddings), and transforming this into a large collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from word-embedding space into TF-IDF space. Further more, it would be interesting to see which words would be selected, and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
\end{document}
